Results Analysis

### 2024-04-24 analysis/resultsAnalysis.Rmd
added figures

randomPPC
```

Calculate confidence interval for explicitly stated PPC policies among randomly selected journals
```{r}

randomPPCyes <- dj_random %>%
  filter(ppc_type == 'A', !is.na(ppc_name)) %>%
  summarise(count = n())

@@

>>>>

randomPPC
```
Get the names of the randomly selected journals that have 'NO EXPLICIT' PPC options
```{r}
dj_random %>%
  filter(ppc_type == "A" & has_ppc == "NO EXPLICIT") %>%
  print()
```

Calculate confidence interval for explicitly stated PPC policies among randomly selected journals
```{r}
randomPPCyes <- dj_random %>%
  filter(ppc_type == 'A', !is.na(ppc_name)) %>%
  summarise(count = n())

@@

# FIGURES

```{r}
quantLength <- d_journals %>%
 select(c(sample_id, ppc_name, ppc_length)) %>%
 filter(!is.na(ppc_length),
         ppc_length != "NOT STATED",
         ppc_length != "Qualitative") %>%
 mutate(Length = as.numeric(ppc_length))

quantLength %>%  
 ggplot(mapping = aes(x = ppc_name, y = Length, colour = sample_id)) +
 geom_boxplot(
    color = "black",
    fill = "lightblue",
    alpha = 0.5
 ) +
 geom_jitter(width = 0.2) + 
 coord_flip() +
 theme_bw() +
 labs(Title = "Length Limits", x = "Post-publication critique type", y = "Length limits (words)")

```{r}
quantTime <- d_journals %>%
 select(c(sample_id, ppc_name, ppc_time)) %>%
 filter(!is.na(ppc_time),
         ppc_time != "NOT STATED",
         ppc_time != "Qualitative") %>%
 mutate(Time = as.numeric(ppc_time))

quantTime %>%  
 ggplot(mapping = aes(x = ppc_name, y = Time, colour = sample_id)) +
 geom_boxplot(
    color = "black",
    fill = "lightblue",
    alpha = 0.5
 ) +
 geom_jitter(width = 0.2) + 
 coord_flip() +
 theme_bw() +
 labs(Title = "Time Limits", x = "Post-publication critique type", y = "Time limits (weeks)")
```
